### 2022-09-17 main/chapter_searches.tex
add words about discovery regions; very beginning of significance

\paragraph{Exclusion fits.}
Model-dependent `exclusion' fits add simulated yields from precisely
defined models to the \heplikelihood\ model.
These fits can use multiple signal regions simultaneously, and couple the
effect of parametrized modifications to the signals and backgrounds between
the bins of those regions.
% cls
% parameter plane
% exclusion contours
\TODO{Exclusion (model-dependent signal}
% CLs

\paragraph{Discovery fits.}
\TODO{Discovery (model-independent signal)}

model-independent `discovery' fits, which add a variable signal yield to one
signal region in isolation.

% CLs and p-value
% maximum likelihood ratio test statistics
% despite likeliy superiority of $n$

\subsection{Gaussian significance}

\TODO{significance}

@@

% tail area

% maximum likelihood ratio

% similarity and difference

>>>>

\paragraph{Exclusion fits.}
Model-dependent `exclusion' fits add simulated yields from precisely
defined models to the \heplikelihood\ model.
These fits can use multiple signal regions simultaneously, and couple the
effect of parametrized modifications to the signals and backgrounds between
the bins of those regions.

From exclusion fits, we extract statistical results with the $\cls$ method to
mark individual models as excluded and set limits on their production
cross-sections.
For presentation on paper, articles consider two-dimensional planes of model
parameters and present contiguous `exclusion contours' within which all models
are marked as excluded at a given level.

\paragraph{Discovery fits.}
Model-dependence sacrifices some generality.
Model-independent `discovery' fits are therefore performed to extract results
that could be interpretable for any hypothesized model.
These fits include the control regions and only one signal region, a
discovery region, in which a flat signal yield is considered.
The $\cls$ method is again used to set limits on that signal yield,
and a `discovery' \pvalue\ is also computed with the intention to quantify
the significance of a data excess were one observed.

Despite the likely superiority of $t(n) = n$ test statistics for these
single-bin signal-plus-background experiments, standard maximum likelihood
ratio test statistics are used, and may explain quirks in the discovery
region results that we shall see in the results of
Chapter~\ref{chapter:2ljets}.

\subsection{Gaussian significance}
Standard-deviations distance is a more intuitive measure of compatibility than
a \pvalue.

\TODO{tail area}

\TODO{log maximum likelihood ratio}

\TODO{significance measures}

@@

% similarity and difference?? TODO
